<!-- badges go here -->
[![Say Thanks!](https://img.shields.io/badge/Say%20Thanks-!-1EAEDB.svg)](https://saythanks.io/to/JohnCoene)
[![Travis build status](https://travis-ci.org/news-r/guardian.svg?branch=master)](https://travis-ci.org/news-r/guardian)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/news-r/guardian?branch=master&svg=true)](https://ci.appveyor.com/project/news-r/guardian)
<!-- badges: end -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  collapse = TRUE,
  comment = "#>"
)

library(htmltools)
```

```{r, echo=FALSE}
br()
br()

div(
  class = "row",
  div(
    class = "col-md-4",
    img(
      src = "logo.png",
      class = "img-responsive responsive-img"
    )
  ),
  div(
    class = "col-md-8",
    p(
      "Access over 2 million pieces of content from The Guardian."
    ),
    p(
      tags$a(
        tags$i(class = "fa fa-code"),
        class = "btn btn-primary",
        href = "reference/index.html",
        style = "margin-bottom: 5px;",
        "Reference"
      ),
      tags$a(
        tags$i(class = "fa fa-github"),
        class = "btn btn-default",
        href = "https://github.com/news-r/guardian",
        style = "margin-bottom: 5px;",
        "Repository"
      )
    )
  )
)
```

## Installation

You can install the package with `remotes` from Github, see [changes](news/index.html).

```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_github("news-r/pkg") # github
```

## Setup

To get started, You need a [free API key](https://open-platform.theguardian.com/access/). Then either specify the aforementioned key using `guardian_key` or specify it as environment variable (likely in your .Renviron) as `GUARDIAN_API_KEY`.

```r
guardian_key("xxXXxxXx")
```

## Example

The package revolves around the following principle, first create your API calls then execute them with `gd_call`. This is because the package is built upon the [async package](https://github.com/r-lib/async) which lets you execute API calls asynchonously: the (free) developer plan allows you to do up to 12 calls per second. 

Below we look for 15 pages of articles on "Brexit".

```{r}
library(guardian)

# search for brexit articles
(to_search <- gd_search("brexit", pages = 15))

# actually execute 15 calls (1 per page)
results <- gd_call(to_search)
head(results)
```
