---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
<!-- badges: start -->
[![Travis build status](https://travis-ci.org/news-r/guardian.svg?branch=master)](https://travis-ci.org/news-r/guardian)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/news-r/guardian?branch=master&svg=true)](https://ci.appveyor.com/project/news-r/guardian)
<!-- badges: end -->

# guardian

Access over 2 million pieces of content from [The Guardian](https://www.theguardian.com/)

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("news-r/guardian")
```

## Setup

To get started, You need a [free API key](https://open-platform.theguardian.com/access/). Then either specify the aforementioned key using `guardian_key` or specify it as environment variable (likely in your .Renviron) as `GUARDIAN_API_KEY`.

```r
guardian_key("xxXXxxXx")
```

## Example

The package revolves around the following principle, first create your API calls then execute them with `gd_call`. This is because the package is built upon the [async package](https://github.com/r-lib/async) which lets you execute API calls asynchonously: the (free) developer plan allows you to do up to 12 calls per second. 

Below we look for 15 pages of articles on "Brexit".

```{r}
library(guardian)

# search for brexit articles
(to_search <- gd_search("brexit", pages = 15))

# actually execute 15 calls (1 per page)
results <- gd_call(to_search)
head(results)
```
